\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-06-17 popl-2019-journal-v/discussion.tex
[POPLjv] Add TODO comments to discussion and related work

%\subsection{Sharing the stack}
% ?
\subsection{Practical Applicability}
We believe there are good arguments for practical applicability of \stktokens{}.
The strong security guarantees are proven in a way that is reusable as part of a bigger proof of compiler security.
Its costs are
\begin{itemize}
\item a constant and limited amount of checks on every boundary crossing.
\item possibly a small memory overhead because stack frames must be of non-zero length
\end{itemize}
The main caveat is that we rely on the assumption that capability machines like CHERI can be extended with linear capabilities in an efficient way.

@@

>>>>

%\subsection{Sharing the stack}
% ?

\begin{jversion}
  A compiler is fully abstract when it enforces all high-level properties of a high-level language which means that the high-level language that dictates what we need to enforce.
  In other words to figure out what properties we want, we need to figure out what high-level language we want.
  % TODO is this all we have to say about high-level properties? Maybe something about address hiding and the potential issues. Also other notions of control-flow, e.g. call/CC
  % TODO say something about horizontal vs vertical composition.

  % TODO new paragraph: conditional full-abstraction

  % TODO new paragraph: Machine checked proof. MANY details, any future work should be machine checked.

  % TODO new subsection on construction of overlay semantics:
  % If we don't, we will have to come up with new syntax. Further, say we had
  % introduced new instruction, how would we do the back translation? We would not
  % be able to tell whether a series of instructions came from a call or a series of
  % instructions that just look like a call. With this approach everything that
  % looks like a call is a call. The back translation is simply the identity making
  % things a lot easier.

\end{jversion}

\subsection{Practical Applicability}
We believe there are good arguments for practical applicability of \stktokens{}.
The strong security guarantees are proven in a way that is reusable as part of a bigger proof of compiler security.
Its costs are
\begin{itemize}
\item a constant and limited amount of checks on every boundary crossing.
\item possibly a small memory overhead because stack frames must be of non-zero length
\end{itemize}
The main caveat is that we rely on the assumption that capability machines like CHERI can be extended with linear capabilities in an efficient way.

@@

% TODO passing pointers for stack allocated memory is not possible with linear stack
